\documentclass[12pt]{article}  
%%Read the manual for other options. 

\pagestyle{empty} %%Eliminates page numbers
%%\input rmb_macros
%%Collect your favorite macros in a 
%%separate file

%\input amssym.def
%\input amssym
%\input mssymb
%%Defines additional symbols



\usepackage{graphics}
\usepackage{amsmath,amssymb,amsthm, multicol, systeme}
\usepackage[pdftex]{graphicx}
\usepackage{epsf}
%%Use to include pictures. 

%\newcommand{\comment}[1]{}
%\newcommand{\sobolev}[2]{W^{#1,#2}}
%\newcommand{\sobolev}[2]{L^#2_#1}
%%Some examples of macros or new commands.

\addtolength{\oddsidemargin}{-.75in}
\addtolength{\evensidemargin}{-.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{2.25in}
\sysdelim..
%%Set margins, defaults are ok. 

\begin{document}
\begin{center}
{\bf \Large Row Reduction and Echelon Forms}
\vspace{0.2cm}
\hrule
\end{center}

\begin{multicols*}{2}
	\begin{enumerate}
		\item Consider each matrix as the augmented matrix of a linear system. What are the next two row operations that should be performed in the process of solving the system? Finish solving the system.
		\begin{enumerate}
			\item \[
			\begin{bmatrix}
				5 & 1 & 0 & 13\\
				1 & -4 & 0 & -10\\
				0 & 3 & -1 & 5
			\end{bmatrix}
			\]
			\vfill
			\item \[
			\begin{bmatrix}
				1 & -6 & 4 & 0 & -1\\
				0 & 2 & -7 & 0 & 3\\
				0 & 0 & 1 & 2 & -3\\
				0 & 0 & 3 & 1 & 6
			\end{bmatrix}
			\]
			\vfill
		\end{enumerate}

		\item Solve the systems.
		\begin{enumerate}
			\item \systeme{
			x_2 + 4x_3 = -5,
			x_1 + 3x_2 + 5x_3 = -2,
			3x_1+7x_2 + 7x_3 = 6
			}

			\vfill

			\item \systeme{
			x_1 - 3x_2 = 5,
			-x_1 + x_2 + 5x_3 = 2,
			x_2 + x_3 = 0
			}
		\end{enumerate}
		\vfill
		\item Do the three planes $x+2y+z=4$, $y-z=1$, and $x+3y=0$ have at least one common point of intersection?
		\vfill\null\columnbreak

		\item Suppose $a,b,c,$ and $d$ are constants such that $a$ is nonzero and the system below is consistent for all possible values of $f$ and $g$. What can you say about the numbers $a,b,c$, and $d$?
		\[
		\begin{array}{rcrcr}
			ax_1 & + & bx_2 & = & f\\
			cx_1 & + & dx_2 & = & g	
		\end{array}
		\]
		\vfill

		\item Row reduce the matrix to reduced echelon form. Circle the pivot positions in the final matrix and in the original matrix and list the pivot columns.
		\[
		\begin{bmatrix}
			1 & 3 & 5 & 7\\
			3 & 5 & 7 & 9\\
			5 & 7 & 9 & 1
		\end{bmatrix}
		\]
		\vfill

		\item Find the general solutions of the system whose augmented matrices are given here.
		\begin{enumerate}
			\item \[
			\begin{bmatrix}
				1 & 4 & 0 & 7\\
				2 & 7 & 0 & 10
			\end{bmatrix}
			\]
			\vfill
			\item \[
			\begin{bmatrix}
				1 & -7 & 0  & 6 & 5\\
				0 & 0 & 1 & -2 & -3\\
				-1 & 7 & -4 & 2 & 7
			\end{bmatrix}
			\]
			\vfill
		\end{enumerate}

		\item Determine the value(s) of $h$ such that the matrix is the augmented matrix of a consistent linear system.
		\begin{enumerate}
			\item 
			\[
			\begin{bmatrix}
				1 & 1 & h & 1\\
				1 & h & 1 & 1\\
				h & 1 & 1 & 1
			\end{bmatrix}
			\]
		\end{enumerate}
		\vfill\null\pagebreak

		\item Choose $h$ and $k$ such that the system has (a) no solution, (b) a unique solution, and (c) many solutions.
		\[
		\begin{array}{rcrcr}
			x & + & 3y & = & 2\\
			3x & + & hy & = & k
		\end{array}
		\]
		\vfill

		\item True or False? Justify.
		\begin{enumerate}
			\item If one row in an echelon form of an augmented matrix is $[0\ 0\ 0\ 5\ 0]$, then the associated linear system is inconsistent.
			\vfill
			\item The echelon form of a matrix is unique.
			\vfill
			\item Whenever a (consistent) system has free variables, the solution set contains many solutions.
			\vfill
		\end{enumerate}

		\item Suppose the coefficient matrix of a system of linear equations has a pivot position in every row. Explain why the system is consistent.
		\vfill
	\end{enumerate}
\end{multicols*}

\end{document}