\documentclass[12pt]{article}  
%%Read the manual for other options. 

\pagestyle{empty} %%Eliminates page numbers
%%\input rmb_macros
%%Collect your favorite macros in a 
%%separate file

%\input amssym.def
%\input amssym
%\input mssymb
%%Defines additional symbols



\usepackage{graphics}
\usepackage{amsmath,amssymb,amsthm, multicol,mathtools}
\usepackage[pdftex]{graphicx}
\usepackage{epsf}
%%Use to include pictures. 

%\newcommand{\comment}[1]{}
%\newcommand{\sobolev}[2]{W^{#1,#2}}
%\newcommand{\sobolev}[2]{L^#2_#1}
%%Some examples of macros or new commands.

\addtolength{\oddsidemargin}{-.75in}
\addtolength{\evensidemargin}{-.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{2.25in}
%%Set margins, defaults are ok. 

\begin{document}
\begin{center}
{\bf \Large Linear Equations}
\vspace{0.2cm}
\hrule
\end{center}

\begin{multicols*}{2}
	\begin{enumerate}
		\item What does it mean for a linear system to be consistent? Give an example of a consistent system and an example of an inconsistent system.
		\vfill

		\item One of the fundamental row operations is scaling: we can multiply all entries in a row by a nonzero constant. Why is it important to us that this constant be nonzero?

		\vfill

		\item Come up with a system of two equations in two unknowns that satisfies the following constraint, if possible. If no such system exists, try to explain why.
		\begin{enumerate}
			\item The system has exactly one solution.
			\vfill
			\item The system has no solution.
			\vfill
			\item The system has infinitely many solutions.
			\vfill
			\item The system has exactly two solutions.
			\vfill\null
		\end{enumerate}
		\columnbreak
		\item Solve the system using elementary row operations on the equations or on the augmented matrix.
		\[
		\begin{array}{ccccc}
			3x_1 &+&6x_2&=&-3\\
			5x_1&+&7x_2&=&10
		\end{array}
		\]
		\vfill

		\item What are the next few row operations that should be performed in the process of solving the system?
		\begin{enumerate}
			\item
			\[
			\begin{bmatrix*}[r]
				1 & -6 & 4 & 0 & -1\\
				0 & 2 & -7 & 0 & 4\\
				0 & 0 & 1 & 2 & -3\\
				0 & 0 & 4 & 1 & 2
			\end{bmatrix*}
			\]
			\vfill
			\item \[
			\begin{bmatrix*}[r]
				1 & 7 & 3 & -4\\
				0 & 1 & -1 & 3\\
				0 & 0 & 0 & 1\\
				0 & 0 & 1 & -2
			\end{bmatrix*}
			\]
			\vfill
		\end{enumerate}
		\item Perform a substitution to turn the system of equations into a linear system and then solve it.
		\begin{enumerate}
			\item \[
			\begin{array}{ccccc}
				-2\sin t & -& 2\cos s & = & -1\\
				2\sin t & + & \cos s & = & 1
			\end{array}
			\]
			\vfill
			\item \[
			\begin{array}{ccccc}
				\sqrt{x} & - & e^y &=&1\\
				2\sqrt{x}&-&e^y &=&5
			\end{array}
			\]
			\vfill\null\pagebreak
		\end{enumerate}

		\item Determine if the system is consistent.
		\[
		\begin{array}{ccccccccc}
			2x_1&&&&&-&4x_4&=&-10\\
			&&3x_2&+&3x_3&&&=&0\\
			&&&&x_3&+&4x_4&=&-1\\
			-3x_1&+&2x_2&+&3x_3&+&x_4&=&5
		\end{array}
		\]
		\vfill

		\item Determine the value(s) of $h$ such that the matrix is the augmented matrix of a consistent linear system.
		\begin{enumerate}
			\item \[
			\begin{bmatrix*}[r]
				1&h&-5\\
				2&-8&6
			\end{bmatrix*}
			\]
			\vfill
			\item \[
			\begin{bmatrix*}[r]
				-4 & 12 & h\\
				2 & -6 & -3
			\end{bmatrix*}
			\]
			\vfill
		\end{enumerate}

		\item Suppose $a$, $b$, $c$, and $d$ are constants such that $a$ is not zero and the system below is consistent for all possible values of $f$ and $g$. What can you say about the numbers $a$, $b$, $c$, and $d$?
		\[
		\begin{array}{ccccc}
			ax_1 &+&bx_2&=&f\\
			cx_1&+&dx_2&=&g
		\end{array}
		\]
		\vfill
	\end{enumerate}
\end{multicols*}

\end{document}