%% Please change the file name by replacing N with the apporpriate number
%% corresponding to the current homework and XX with your initials.
%% https://www.math.uci.edu/~gpatrick/jsOnline/hw1.html

\documentclass[11pt,letterpaper]{report}
\usepackage{amssymb,amsfonts,color,graphicx,amsmath,enumerate}
\usepackage{tikz} %This package offers the ability to draw pictures
\usepackage{amsthm}

\newcommand{\naturals}{\mathbb{N}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\complex}{\mathbb{C}}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\exreals}{\overline{\mathbb{R}}}
\newcommand{\mcal}[1]{\mathcal{#1}}
\newcommand{\mable}{measurable}
\newcommand{\quats}{\mathbb{H}}
\newcommand{\rationals}{\mathbb{Q}}
\newcommand{\norm}{\trianglelefteq}
\newcommand{\Aut}{\text{Aut}}
\newcommand{\disk}{\mathbb{D}}
\newcommand{\halfplane}{\mathbb{H}}
\newcommand{\Lp}[2]{\left\|{#1}\right\|_{L^{#2}}}
\newcommand{\supp}[1]{\text{supp}({#1})}
\newcommand{\Hom}[2]{\text{Hom}_{{#1}}({#2})}
\newcommand{\tr}{\text{tr}}
\newcommand{\field}{\mathbb{F}}
\newcommand{\Gal}[1]{\text{Gal}\left({#1}\right)}
\newcommand{\esssup}{\text{ess sup }}
\newcommand{\essinf}{\text{ess inf }}
\newcommand{\affine}{\mathbb{A}}

\newenvironment{solution}
{\begin{proof}[Solution]}
{\end{proof}}

\voffset=-3cm
\hoffset=-2.25cm
\textheight=24cm
\textwidth=17.25cm
\addtolength{\jot}{8pt}
\linespread{1.3}

\begin{document}
%\noindent{\em Liam Hardiman\hfill{Date} }
% Please give relevant information
\begin{center}
{\bf \Large Algebra Qualifying Exam - Fall 2018} %Replace N with the appropriate number
\vspace{0.2cm}
\hrule
\end{center}

\begin{enumerate}
	\item Let $G$ be a group of size 42.
	\begin{enumerate}
		\item Prove that $G$ has a subgroup $H$ of order 6 and any two such subgroups are conjugate in $G$.
		\item Deduce that $G = H\ltimes N$, where $N$ is a normal subgroup of order 7.
	\end{enumerate}
	\vfill
	\item Let $p$ be a prime. Show that for any Sylow $p$-subgroup $H\subset GL_n(\field_p)$ there exists a basis in the vector space $V= \field_p^n$ such that $H$ consists of $\field_p$-linear maps given, in that basis, by an upper-triangular matrix with 1 on the diagonal.
	\vfill
	\item For a group $G$, let $G_1 = G$ and let $G_{n+1}:= [G, G_n]$. We say that $G$ is nilpotent if $G_N = 1$ for some $N$. Prove that if $G$ is a $p$-group, i.e. $|G| = p^r$ for some prime $p$, then $G$ is nilpotent.
	\vfill
	\item Let $R\subset \rationals$ be the subring in the field of rational numbers, given by the fractions $\frac{a}{b}$ with $a\in \integers$ and $b = 2^k3^l$ with $k,l\geq 0$. Describe the ideals of $R$. Is $R$ a PID?
	\vfill
	\item Let $S = \{a+bi: a,b\in \integers\}\subset \complex$ be the ring of Gaussian integers.
	\begin{enumerate}
		\item Show that $S$ is a Euclidean domain.
		\item Find a decomposition of $a = 11\in S$ into a product of irreducibles in $S$.
		\item Find a decomposition of $b=13\in S$ into a product of irreducibles in $S$. 
	\end{enumerate}
	\vfill
	\item Let $V$ be a nonzero finite-dimensional vector space over the complex numbers.
	\begin{enumerate}
		\item If $S$ and $T$ are commuting linear operators on $V$, prove that each eigenspace of $S$ is mapped into itself by $T$.
		\item Let $A_1, \ldots, A_k$ be finitely many linear operators on $V$ that commute pairwise. Prove that they have a common eigenvector in $V$.
		\item If $V$ has dimension $n$, show that there exists a nested sequence of subspaces
		\[
		0 = V_0 \subset V_1\subset \cdots \subset V_n = V,
		\]
		where each $V_j$ has dimension $j$ and is mapped into itself by each of the operators $A_1, \ldots, A_k$.
	\end{enumerate}
	\vfill\null\pagebreak

	\item Let $A$ be an $n\times n$ matrix with complex coefficients and assume that every eigenvalue $\lambda$ of $A$ satisfies $Im(\lambda)>0$. Consider the $(2n)\times (2n)$ matrix
	\[
	B = \begin{bmatrix}
		A & 0\\
		0 & \overline{A}
	\end{bmatrix}.
	\]
	Find the invariant factors of $B$ in terms of invariant factors of $A$ and prove that $B$ is similar to a real-valued matrix.
	\vfill
	\item Find the Galois group of $x^6-2$ over $\rationals$ and over $\field_5$.
	\vfill
	\item Let $K/F$ be a finite Galois algebraic extension with no proper intermediate fields. Prove that $[K:F]$ is prime.
	\vfill
	\item Let $Q$ denote the quaternion group, i.e.
	\[
	Q = \{\pm 1, \pm i, \pm j, \pm k\}
	\]
	with $i^2 = j^2= k^2 = ijk = -1$, $-1\in Z(Q)$ and $(-1)^2 = 1$.
	\begin{enumerate}
		\item Classify the conjugacy classes of $Q$.
		\item Construct the character table of $Q$.
	\end{enumerate}
	\vfill
\end{enumerate}

\end{document}