\documentclass[12pt]{article}  
%%Read the manual for other options. 

\pagestyle{empty} %%Eliminates page numbers
%%\input rmb_macros
%%Collect your favorite macros in a 
%%separate file

%\input amssym.def
%\input amssym
%\input mssymb
%%Defines additional symbols



\usepackage{graphics}
\usepackage{amsmath,amssymb,amsthm, multicol,mathtools}
\usepackage[pdftex]{graphicx}
\usepackage{epsf}
%%Use to include pictures. 

%\newcommand{\comment}[1]{}
%\newcommand{\sobolev}[2]{W^{#1,#2}}
%\newcommand{\sobolev}[2]{L^#2_#1}
%%Some examples of macros or new commands.

\addtolength{\oddsidemargin}{-.75in}
\addtolength{\evensidemargin}{-.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{2.25in}
%%Set margins, defaults are ok. 

\begin{document}
\begin{center}
{\bf \Large Matrix Inversion}
\vspace{0.2cm}
\hrule
\end{center}

%Section 2.2: 2,3,6,9,13,14,19,21,31,32

%Section 2.3: 2,5,8,11,12,13,16,18,19,23,28

\begin{multicols*}{2}
	\begin{enumerate}
		\item Find the inverses of the matrices (i) by using the formula for the inverse of a 2 by 2 matrix and (ii) by row reduction.
		\[
		\text{(a)}\quad \begin{bmatrix}
			8 & 6\\
			5 & 4
		\end{bmatrix}\qquad\text{(b)}\quad
		\begin{bmatrix}
			3 & -4\\
			7 & -8
		\end{bmatrix}
		\]
		\vfill

		\item Solve the system of equations using matrix inversion.
		\[
		\begin{array}{rcrcr}
			2x & + & y & = & 1\\
			-3x & +&2y & = & 0
		\end{array}
		\]
		\vfill
		\item True or False? Explain.
		\begin{enumerate}
			\item A product of invertible $n\times n$ matrices is invertible, and the inverse of the product is the product of the inverses.
			\vfill
			\item If $A$ is invertible, then so is $A^{-1}$ and the inverse of $A^{-1}$ is $A$.
			\vfill
			\item If $A = \begin{bmatrix}a&b\\c&d\end{bmatrix}$ and $ad=bc$ then $A$ is not invertible.
			\vfill
			\item If $A$ can be row reduced to the identity matrix, then $A$ must be invertible.
			\vfill
			\item If $A$ is invertible, then elementary row operations that reduce $A$ to the identity matrix also reduce $A^{-1}$ to the identity matrix.
		\end{enumerate}
		\vfill\null\columnbreak

		\item Let $A$ be an invertible $n\times n$ matrix, and let $B$ be an $n\times p$ matrix. Show that the equation $AX=B$ has a unique solution $A^{-1}B$.
		\vfill

		\item Suppose $A$ and $B$ are $n\times n$, $B$ is invertible, and $AB$ is invertible. Show that $A$ is invertible.
		\vfill

		\item Explain why the columns of an $n\times n$ matrix span $\mathbb{R}^n$ when $A$ is invertible.
		\vfill

		\item Find the inverses of the matrices by row reduction.
		\begin{enumerate}
			\item \[
			\begin{bmatrix*}[r]
				3 & 0 & 2\\
				2 & 0 & -2\\
				0 & 1 & 1
			\end{bmatrix*}
			\]
			\vfill

			\item \[
			\begin{bmatrix*}[r]
				0 & -3 & -2\\
				1 & -4 & -2\\
				-3 & 4 & 1	
			\end{bmatrix*}
			\]
		\end{enumerate}
		\vfill\null\pagebreak
		%Section 2.3: 2,5,8,11,12,13,16,18,19,23,28

		\item Determine whether the matrices are invertible using as few computations as possible.
		\begin{enumerate}
			\item \[
			\begin{bmatrix*}[r]
				5 & 7\\
				-3 & -6
			\end{bmatrix*}
			\]
			\vfill
			\item \[
			\begin{bmatrix*}[r]
				-7 & 0 & 4\\
				3 & 0 & -1\\
				2 & 0 & 9	
			\end{bmatrix*}
			\]
			\vfill
			\item \[
			\begin{bmatrix*}[r]
				-1 & -3 & 0 & 1\\
				3 & 5 & 8 & -3\\
				-2 & -6 & 3 & 2\\
				0 & -1 & 2 & 1
			\end{bmatrix*}
			\]
		\end{enumerate}
		\vfill

		\item An $m\times n$ matrix is lower triangular if all of its entries lying above the main diagonal are zero. When is a square lower triangular matrix invertible?

		\vfill

		\item Can a square matrix with two identical columns be invertible?
		\vfill

		\item If $A$ is invertible, then the columns of $A^{-1}$ are linearly independent. Why?

		\vfill\null\columnbreak

		\item If the equation $Gx = y$ has more than one solution for some $y\in \mathbb{R}^n$, can the columns of $G$ span $\mathbb{R}^n$?
		\vfill

		\item Explain why the columns of $A^2$ span $\mathbb{R}^n$ whenever the columns of $A$ are linearly independent.
		\vfill

		\item If $A$ is an $n\times n$ matrix and the transformation $x\mapsto Ax$ is one-to-one, is it necessarily also onto? What if $x\mapsto Ax$ is onto. Then is it one-to-one too?

		\vfill

	\end{enumerate}	
\end{multicols*}

\end{document}